Stochastic Approximation Monte Carlo with a Dynamic Update Factor (SAD)

### 2018-09-28 papers/histogram/sad.tex
abstract update for paper.

\begin{document}
\title{Stochastic Approximation Monte Carlo with Dynamic Update
Factor (SAD)
}

@@

\begin{abstract}
  We present several histogram methods and compare the performance and
  efficiency at treating the square-well fluid.
\end{abstract}

>>>>

\begin{document}
\title{Stochastic Approximation Monte Carlo with a Dynamic Update
Factor (SAD)
}

@@

\begin{abstract}
  We present a novel Monte-Carlo algorithm based on Stochastic
  Approximation Monte Carlo (SAMC) algorithm for directly calculating
  the density of states. The proposed method is Stochastic
  Approximation with a dynamic update factor (SAD-$\gamma$ or SAD)
  dynamically adjusts the update factor $\gamma$ during the course of
  the simulation. We test this MC method on the square-well fluid and
  compare the convergence time and entropy error for a variety of weight-based
  and transition matrix Monte-Carlo methods. SAD rapidly converges to the
  correct density of states without the need for the user to specify an
  arbitrary tunable parameter $t_0$ as in the case of SAMC.
\end{abstract}
